Paper Analysis

### 2025-05-01 Paper_WriteUp/Paper_Plots.qmd
moving permutation section to appendix

# #save magnus
ggsave(plot = ppd_rating_plot,
       filename = here("Paper_WriteUp", "paper_figures", "fig7a.png"), dpi = 1000,
       height = 4, width = 6)
# #save nihal
# ggsave(plot = ppd_rating_plot,
#        filename = here("Paper_WriteUp", "paper_figures", "fig7b.png"), dpi = 1000,
#        height = 4, width = 6)
```

>>>>

# #save magnus
# ggsave(plot = ppd_rating_plot,
#        filename = here("Paper_WriteUp", "paper_figures", "fig7a.png"), dpi = 1000,
#        height = 4, width = 6)
# #save nihal
# ggsave(plot = ppd_rating_plot,
#        filename = here("Paper_WriteUp", "paper_figures", "fig7b.png"), dpi = 1000,
#        height = 4, width = 6)
```
